\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{varwidth}
\usepackage{xcolor}
\usepackage{listings}


\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{CStyle}{
	language=C++,
	backgroundcolor=\color{backcolour},   
	commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegray},
	stringstyle=\color{codepurple},
	basicstyle=\ttfamily\footnotesize,
	breakatwhitespace=false,         
	breaklines=true,                 
	keepspaces=true,                 
	numbers=left,       
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2,
}
\lstset{style=CStyle}

\title{Lab 7 Report \\ \large EEL4742C - 00446}
\author{Yousef Awad}
\date{September 2025}
\setcounter{secnumdepth}{0}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Introduction}
In this lab, we learned how to use the I2C module on the MSP430 as well as what I2C is generally, via programming the I2C link that connects the board to the booster pack that we put on it.

\section{7.1 I2C Transmission}
\lstinputlisting{7_1.c}
\pagebreak
\section{7.2 Reading Measurements from the Light Sensor}
\lstinputlisting{7_2.c}
\pagebreak
\section{7.3 Application: Lux Logger}
\lstinputlisting{7_3.c}
\pagebreak
\pagebreak
\section{Student Q\&A}
\subsection{1}
\textbf{Given:} The light sensor has an address pin that allows customizing the I2C address. How many addresses are possible? What are they and how are they configured? Look in the sensor’s data sheet.
\newline
\newline
NEED TO ANSWER

\subsection{2}
\textbf{Given:} According to the light sensor’s data sheet, what should be the value of the pull-up resistors on the I2C wires? Did the BoosterPack use the same values?
\newline
\newline
NEED TO ANSWER

\subsection{3}
\textbf{Given:} What I2C clock frequency do each of the eUSCI module and the sensor support?
\newline
\newline
NEED TO ANSWER

\end{document}
